A generalized definition of multidimensional item response theory parameters

### 2024-07-24 output/paper_draft/paper_M2PLM_parameters.Rmd
Expresses direction correctly in the test space

The measurement direction is given by the signs of $`r DIR_COS_ITEM_VEC`$ which,
also due to the strict positiveness of $`r MDISC_SYM`$,
are equal to the signs of $`r DISCR_VECTOR`$.
This property leads directly to generalizing
the parameters to the monotonically non-increasing case:
The measurement direction relative to dimension $`r DIM_INDEX`$
will be negative when $`r IRF_ABBR`$ is monotonically decreasing
with respect to variations along $`r TRAIT_COMPONENT`$.
When $`r IRF_ABBR`$ is constant
with respect to variations along $`r TRAIT_COMPONENT`$,
$`r SIGN_COS_VEC_ITEM_EQ`$,
which means that $`r MIL_PARAM`$ is orthogonal to the $`r DIM_INDEX`$-th axis.
However, note that this does not necessarily imply that
the vector is parallel to any other axis
(or strictly contained in the hyperplane formed by other axes, for that matter);
this will always be true for the $`r MIL_AG_PARAM`$ due to
the orthogonality assumption,
but it will depend on the correlation matrix $`r CORR_MATRIX`$
for the other two versions of the parameter.

>>>>

The measurement direction is given by
the signs of $`r DIR_COS_ITEM_VEC_BASIS_TS`$ which,
also due to the strict positiveness of $`r MDISC_SYM`$,
are equal to the signs of $`r DISCR_VECTOR`$.
This property leads directly to generalizing
the parameters to the monotonically non-increasing case:
The measurement direction relative to dimension $`r DIM_INDEX`$
will be negative when $`r IRF_ABBR`$ is monotonically decreasing
with respect to variations along $`r TRAIT_COMPONENT`$.
When $`r IRF_ABBR`$ is constant
with respect to variations along $`r TRAIT_COMPONENT`$,
$`r SIGN_COS_VEC_ITEM_EQ`$,
which means that $`r MIL_PARAM`$ is orthogonal to the $`r DIM_INDEX`$-th axis.
However, note that this does not necessarily imply that
the vector is parallel to any other axis
(or strictly contained in the hyperplane formed by other axes, for that matter);
this will always be true for the $`r MIL_AG_PARAM`$ due to
the orthogonality assumption,
but it will depend on the correlation matrix $`r CORR_MATRIX`$
for the other two versions of the parameter.
